Appendix

### 2016-08-24 finalwriteup/Appendix.rmd

Example results from:

@@

###Linear regression

@@

all8a = read.csv("report_data/all8a.csv")[,-1]

@@

@@

Example summary of model built with all variables:

@@

# load imputed data
all10mice_f = read.csv("report_data/all10mice_May16.csv")[,-1]

@@

@@

df.blend <- readRDS("report_data/dfblend.rds")

@@

                if ("simp.log" %in% methods) {
                        print("simp.log")
                        fit <- glm(f.rpdol ~ log + rf + boost,
                                   data = train,
                                   family = binomial())

                        pred <- predict(fit, test, type = "response")
                        pred.list[["simp.log"]] = rbind(pred.list[["simp.log"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))

@@

                        pred <- predict(fit, test, n.tree = 6000, type = "response")
                        pred.list[["simp.boost"]] = rbind(pred.list[["simp.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))

@@

                if ("orig.log" %in% methods) { 
                        print("orig.log")
                        pred <- test$log
                        pred.list[["orig.log"]] = rbind(pred.list[["orig.log"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))

@@

                if ("orig.rf" %in% methods) { 
                        print("orig.rf")
                        pred <- test$rf
                        pred.list[["orig.rf"]] = rbind(pred.list[["orig.rf"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))

@@

                if ("orig.boost" %in% methods) { 
                        print("orig.boost")
                        pred <- test$boost
                        pred.list[["orig.boost"]] = rbind(pred.list[["orig.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))

@@

                if ("average" %in% methods) {
                        print("average")
                        pred <- test$model.av
                        pred.list[["average"]] = rbind(pred.list[["average"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))
                }

                if ("FWLS" %in% methods) {
                        print("FWLS")
                        fit <- glm(f.rpdol ~ norm.log + norm.rf + norm.boost + b.timespan.cbrt*norm.log + b.inv.log*norm.log + b.inv.log*norm.rf + Business*norm.boost,
                                   data = train,
                                   family = binomial())
                        pred <- predict(fit, test, type = "response")
                        pred.list[["FWLS"]] = rbind(pred.list[["FWLS"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))
                }

@@

                        pred <- predict(fit, test, n.tree = 6000, type = "response")
                        pred.list[["comp.boost"]] = rbind(pred.list[["comp.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))
                }

                if ("comp.rf" %in% methods) {
                        print("comp.rf")
                        fit <- randomForest(f.rpdol ~ b.timespan.cbrt + no.users + b.inv.log + Business + JD.Second + norm.log + norm.rf + norm.boost,
                                            data = train, mtry = 3, 
                                            ntree = 1000, importance = TRUE
                        )
                        pred <- predict(fit, test, type = "prob")
                        pred <- pred[, 2]
                        pred.list[["comp.rf"]] = rbind(pred.list[["comp.rf"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(k/x.folds.iter),m, sep = "")))
                }

@@

                        plot.roc(pred.p, col = colours[i], print.thres = F)

@@

>>>>

Example results from a single model from each method. This is broken into the three main types of methods that were trialled:

1. Regression models
2. Classification models
3. Blended classification models

@@

### ANOVA regression

@@

all8a = read.csv("all8a.csv")[,-1]

@@

        if(core == FALSE){
        samp = sample.int(nrow(df), 1)                        
        #create sample df - use all variables that are complete from a sample row of data
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','return.pdol',
                                  'code.client', 'code.contact')]
        variables = vars
        } else{
                variables = c('inv.mlsto.log', 'Discipline', 'timespan.cbrt',
                              'no.users', 'pc.pro', 'Business')
        }

@@

Example summary of model built with all variables. Note that each model used a subset of all variables based on the available variables for a randomly selected project:

@@

# load imputed data
all10mice_f = read.csv("all10mice_May16.csv")[,-1]

@@

### Simple Average

@@

df.blend <- readRDS("dfblend.rds")

@@

                if ("simp.log" %in% methods) {
                        print("simp.log")
                        fit <- glm(f.rpdol ~ norm.log + norm.rf + norm.boost,
                                   data = train,
                                   family = binomial())

                        pred <- predict(fit, test, type = "response")
                        pred.list[["simp.log"]] = rbind(pred.list[["simp.log"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

@@

                        pred <- predict(fit, test, n.tree = 6000, type = "response")
                        pred.list[["simp.boost"]] = rbind(pred.list[["simp.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

@@

                if ("orig.log" %in% methods) { 
                        print("orig.log")
                        pred <- test$log
                        pred.list[["orig.log"]] = rbind(pred.list[["orig.log"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

@@

                if ("orig.rf" %in% methods) { 
                        print("orig.rf")
                        pred <- test$rf
                        pred.list[["orig.rf"]] = rbind(pred.list[["orig.rf"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

@@

                if ("orig.boost" %in% methods) { 
                        print("orig.boost")
                        pred <- test$boost
                        pred.list[["orig.boost"]] = rbind(pred.list[["orig.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

@@

                if ("average" %in% methods) {
                        print("average")
                        pred <- test$model.av
                        pred.list[["average"]] = rbind(pred.list[["average"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))
                }

                if ("FWLS" %in% methods) {
                        print("FWLS")
                        fit <- glm(f.rpdol ~ norm.log + norm.rf + norm.boost + b.timespan.cbrt*norm.log + b.inv.log*norm.log + b.inv.log*norm.rf + Business*norm.boost + JD.Second + no.users,
                                   data = train,
                                   family = binomial())
                        pred <- predict(fit, test, type = "response")
                        pred.list[["FWLS"]] = rbind(pred.list[["FWLS"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))
                }

@@

                        pred <- predict(fit, test, n.tree = 6000, type = "response")
                        pred.list[["comp.boost"]] = rbind(pred.list[["comp.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))
                }

                if ("comp.rf" %in% methods) {
                        print("comp.rf")
                        fit <- randomForest(f.rpdol ~ b.timespan.cbrt + no.users + b.inv.log + Business + JD.Second + norm.log + norm.rf + norm.boost,
                                            data = train, mtry = 3, 
                                            ntree = 1000, importance = TRUE
                        )
                        pred <- predict(fit, test, type = "prob")
                        pred <- pred[, 2]
                        pred.list[["comp.rf"]] = rbind(pred.list[["comp.rf"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))
                }

@@

                        plot.roc(pred.p, col = "darkblue", print.thres = F)

@@

simp.av <- iter.auc(mult =1, x.folds.iter = 5, 
                     methods = c("average"),
                     df.iter = df.blend)
auc.func
